An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-12-03 paper/2.minbigul.tex
revise reason for slowness

To close this section,
% In the end of this section, 
let us see the minBiGUL definition of $\textit{bfoldr}$ which is a putback function of an important higher-order function on lists, $\textit{foldr}$:

\smallvspace
$\tab \textit{bfoldr} \ bx = Case \ cond_{sv} \ cond_s \ bx_1 \ bx_2$ where:\\
$\tabs{3} \ cond_{sv} = \lambda (s_1,s_2).\lambda v.(s_1 = [\ ]), \ cond_s = \lambda (s_1,s_2).(s_1 = [\ ])$\\
$\tabs{3} \ bx_1 = RearrV \ g_1 \ g_2 \ bx_v$ where: \\
    $\tabs{4} g_1 = g_2^{-1} = \lambda [v].(v,[\ ]), bx_v = (Skip \ (\lambda \_.())) \times Replace$\\
$\tabs{3} \ bx_2 = RearrS \ f_1 \ f_2 \ bx_s$ where:\\
    $\tabs{4} f_1 = f_2^{-1} = \lambda ((x:xs),e).(x,(xs,e))$, 
$bx_s = ((Replace \times bfoldr \ bx) \circ bx)$
\smallvspace

\noindent In $\textit{bfoldr}$, the composition is inherently left associative, and the number of composition is dynamically determined by the length of the source list. Because~$\circ$ has a higher priority than~$\times$, it is seemingly impossible to transform $\mathit{bfoldr}$ from the left associative composition style to the right one. 
%will look like a composition of many programs at some points in the evaluation if we slow down this process. Since $\circ$ has a higher priority than $\times$, it is seemingly impossible to transform $bfoldr$ from the left associative composition style to the right one.

>>>>

To close this section,
% In the end of this section, 
let us see the minBiGUL definition of $\mathit{bfoldr}$ which is a putback function of an important higher-order function on lists, $\mathit{foldr}$:

\smallvspace
$\tab \mathit{bfoldr} \ bx = Case \ cond_{sv} \ cond_s \ bx_1 \ bx_2$ where:\\
$\tabs{3} \ cond_{sv} = \lambda (s_1,s_2).\lambda v.(s_1 = [\ ]), \ cond_s = \lambda (s_1,s_2).(s_1 = [\ ])$\\
$\tabs{3} \ bx_1 = RearrV \ g_1 \ g_2 \ bx_v$ where: \\
    $\tabs{4} g_1 = g_2^{-1} = \lambda [v].(v,[\ ]), bx_v = (Skip \ (\lambda \_.())) \times Replace$\\
$\tabs{3} \ bx_2 = RearrS \ f_1 \ f_2 \ bx_s$ where:\\
    $\tabs{4} f_1 = f_2^{-1} = \lambda ((x:xs),e).(x,(xs,e))$, 
$bx_s = ((Replace \times bfoldr \ bx) \circ bx)$
\smallvspace

\noindent In $\mathit{bfoldr}$, the composition is inherently left associative, and the number of composition is dynamically determined by the length of the source list. Because~$\circ$ has a higher priority than~$\times$, it is in general not possible to transform $\mathit{bfoldr}$ from the left associative composition style to the right one. 
%will look like a composition of many programs at some points in the evaluation if we slow down this process. Since $\circ$ has a higher priority than $\times$, it is seemingly impossible to transform $bfoldr$ from the left associative composition style to the right one.

### 2019-12-03 paper/5.experiments.tex
revise reason for slowness

Figure \ref{fig:result} 
% illustrates 
shows the evaluation times for each of the seven test cases using the three methods: $put$ in minBiGUL, $put_m$ in minBiGUL$_m$ and $xpg$. We also tried doing similar experiments with $pg$, $cpg$ and $kpg$, but their results are slower than the corresponding ones of $xpg$. Then we simply ignore these tedious results. As we all know, $put$ works poorly for left associative compositions because of the number of reevaluated $get$s.
%The figure shows $put_m$ and $xpg$ are better than $put$ in some cases.
The left part of the figure contains tests using not-large inputs, and we see that $put_m$ is the fastest method for them. However if the input size is large enough, in the cases of the right part of the figure, $put_m$ will be slower quickly due to time for manipulating data in the table. At that time, $xpg$ is 
% proved to be
the most effective method.

>>>>

Figure \ref{fig:result} 
% illustrates 
shows the evaluation times for each of the seven test cases using the three methods: $put$ in minBiGUL, $put_m$ in minBiGUL$_m$ and $xpg$.
We also did similar experiments with $pg$, $cpg$ and $kpg$, but their results are slower than the corresponding ones of $xpg$. The slowness was caused by the exponential number of $pg$ calls in the case of $pg$, redundant evaluations ($cpg$), and redundant overhead for constructing closures ($kpg$).
Then we simply omit these results in Figure \ref{fig:result}.
As we all know, $put$ works poorly for left associative compositions because of the number of reevaluated $get$s.
%The figure shows $put_m$ and $xpg$ are better than $put$ in some cases.
The left part of the figure contains tests using not-large inputs, and we see that $put_m$ is the fastest method for them. However if the input size is large enough, in the cases of the right part of the figure, $put_m$ will be slower quickly due to time for manipulating data in the table. At that time, $xpg$ is 
% proved to be
the most effective method.
